newt change

### 2022-12-06 graphs_newt_snakes/newt_change.Rmd
I created the interrate grade and snake grade file. I ran or re-ran all of the data to look at the correlation between phenotypes as well as other results. Next step I will spend more time exploring these results

newt$info <- "middle"
#need to look into, coloring problem
newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-1-row_num, col_num*row_num-1)] <- "corner"

newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num-row_num), row_num),  c((col_num*row_num-row_num):(col_num*row_num-2)))]   <- "edge"

>>>>

newt$info <- "middle"

#need to look into, coloring problem
newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"

newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"
